%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EXPERIMENTAL RESULTS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%AS-P: 39 flights, 24 this summer
%AS-S1: 9 flights, 9 this summer
A total of 79 hours of flight testing have been performed in 46 flights with the two AtlantikSolar UAVs designed and built at ETH Zurich so far. The following section briefly summarizes the main results required and obtained for efficient long-endurance flight and application of the platform in Search-And-Rescue missions.
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Subsystem level test results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Verification of required level flight power}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%[Philipp]

    - [AS-S1 TFD\#6 F1] power efficiency curves. P\_level from Test flights. Comparison to conceptual design. Describe why power consumption not optimal: e.g. because optimal CD/CL\^1.5 assumed, but this has a) to be met in average and b) even then fluctuations as seen in flight tests are on the order of 2-3 degrees in AOA or +/- 1m/s, so this will never be met perfectly.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Autopilot operation in challenging wind conditions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    

	- gneerell: What weather conditions: Gusts? Wind speeds? Thermal up and downdrafts. all very important at low flight speed.
	e.g. during loitering for power measurements -> very good tracking
	- [AS-S1 TF\#5 F1] show spoiler operation and thermal compliance operation?
	- Later: show waypoint tracking in the ICARUS test paths ...  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Continuous 12hour Flight}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
%[PHILIPP]
   - [AS-S1 TFD\#7]:
   - focus on battery performance. Say that even more possible (mention some results from the lab tests)
   - explain how much autonomous, under which conditions.
  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mapping Flights in Search and Rescue scenarios}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{chapters/4_ExperimentalResults_Reconstruction.tex}
%[DRALEXIS]
%    - mapping missions in ICARUS. 
%    - REF to Separate paper??? Yes, but only once both are accepted.
%   - some cool pics/reconstructed maps